---
title: "Homework 3"
author: "Janavi Kolpekwar"
date: "2025-09-25"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
---

Loading Libraries & Reading in Data
```{r}
library(tidyverse)
library(colorfindr)
library(dplyr)
library(ggplot2)
df <- read.csv("homework3_data.csv")
head(df)
```

Summary Statistics of the Company Data
```{r}
summary(df$sales)
table(df$design)
```

Distinct Color Selection (e-commerce Company of Choice: Etsy)

```{r}
colors_data <- get_colors("~/Desktop/etsyimage.png")
print(colors_data)
```

```{r}
#Etsy company website color selection
custom_colors <- c("#4C3395", "#D7CAFB")
```


Graphical Evidence 1: 
```{r}
# Boxplot of sales by design
df %>%
  mutate(design= factor(design, labels = c("Old", "New"))) %>%
  ggplot(aes(x = design, y = sales, fill = design)) +
  geom_boxplot() +
  scale_fill_manual(values = custom_colors) +
  labs(x = "Website Design (0 = Old, 1 = New)", y = "Sales",
       title = "Distribution of Sales by Website Design") +
  theme_minimal()
```


Graphical Evidence 2: 
```{r}
# Bar chart of average sales and NPS
summary_stats <- df %>%
  group_by(design) %>%
  summarise(
    avg_sales = mean(sales),
    avg_nps   = mean(nps),
    .groups = "drop"
  )

ggplot(summary_stats, aes(x = factor(design), y = avg_sales, fill = factor(design))) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = custom_colors) +
  geom_text(aes(label = round(avg_sales, 2)), vjust = -0.5) +
  labs(x = "Website Design (0 = Old, 1 = New)", y = "Average Sales",
       title = "Average Sales by Website Design") +
  theme_minimal()

```

Estimated Sales Change from the group means:
```{r}
sales_total_stats <- df %>%
  group_by(design) %>%
  summarize(mean_sales = mean(sales), groups = "drop")
sales_total_stats
```
Average Increase in Sales: 
```{r}
avg_sales_increase <- sales_total_stats$mean_sales[2] - sales_total_stats$mean_sales[1]
avg_sales_increase
```

T-test Summary Stat: 
```{r}
t.test(sales ~ design, data=df)
```

Primary Recommendation: 

Alternative Statement: 

Based on the boxplot...

Based on the histogram...

From a statistical standpoint...

This very low p-value indicates...

While the evidence support redesign, it's important to consider the alternative explanations for the observed increase in sales: 




